Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
details in pages 1-14

pNets can encode naturally the notion of input actions as found,
\eg in value-passing CCS 
\cite{Milner89} or of usual point-to-point message passing calculi,
but it also allows 
for more general mechanisms, like gate negotiation in Lotos~\hl{\cite{lotos}}, or broadcast
communications.

@@

\begin{figure}[h]
\begin{mathpar}
    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
  \end{mathpar}
\caption{\TODO{Xudong revert to the previous example}One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
\end{figure}

Our matching/filtering strategy builds some transitions where
the predicates express incompatible constraints. Even if having an
unsatisfiable (symbolic) transition would not be incorrect,
we choose to minimize the open automaton (\ie its number of
transitions and states), by checking the predicates for satisfiability.
In Fig.~\ref{schema:unsat-ot}, we show an 
unsatisfiable open transition 
from the open automaton of our running example. It shows the case where
the failure controller performs a ``$\PortFail$'' action, while the timer
executes a ``$\PortResume$''. The chosen synchronization
vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
with these actions, since it expects $\NameTimer.\PortStart$. This
  mismatch is materialised by the predicate
fragment ``$\mathit{resume}(\true)=\mathit{start}(b_2)$''.

@@

\begin{figure}[t]
  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
  \caption{\TODO{Xudong: revert to the previous example}The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
\end{figure}

>>>>

pNets can encode naturally the notion of input actions as found,
\eg in value-passing CCS 
\cite{Milner89} or of usual point-to-point message passing calculi,
but it also allows 
for more general mechanisms, like gate negotiation in Lotos~\cite{LotosISO89}, or broadcast
communications.

@@

\begin{figure}[h]
\begin{mathpar}
    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
  \end{mathpar}
\caption{One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
\end{figure}

Our matching/filtering strategy builds some transitions where
the predicates express incompatible constraints. Even if having an
unsatisfiable (symbolic) transition would not be incorrect,
we choose to minimize the open automaton (\ie its number of
transitions and states), by checking the predicates for satisfiability.
In Fig.~\ref{schema:unsat-ot}, we show an 
unsatisfiable open transition 
from the open automaton of our running example. It shows the case where
the failure controller performs a ``$\PortFail$'' action, while the timer
executes a ``$\PortResume$''. The chosen synchronization
vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
with these actions, since it expects $\NameTimer.\PortStart$. This
  mismatch is materialised by the predicate
fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.

@@

\begin{figure}[h]
  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
\end{figure}
